---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sds

<!-- badges: start -->
[![R-CMD-check](https://github.com/datalorax/sds-pkg/workflows/R-CMD-check/badge.svg)](https://github.com/datalorax/sds-pkg/actions)
<!-- badges: end -->

The **sds** package is designed to accompany the [Social Data Science with R](https://www.sds.pub) book. It includes a function to load data different datasets and will soon include [learnr](https://rstudio.github.io/learnr/) apps for some of the more introductory content.

## Installation

<!-- You can install the released version of sds from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("sds") -->
<!-- ``` -->

You can install the development version of the package from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("datalorax/sds-pkg")
```
## Example

There are multiple datasets used throughout the book. See all the datasets [here](). We can load any of these datasets using the `get_data()` function, passing the name of the dataset. For example.

```{r example}
library(sds)
benchmarks <- get_data("benchmarks")
benchmarks
```

The `get_data()` function supports any of the following: `"benchmarks"`, `"ds-bowl-2019"`, `"k-entry"`, `"sesame"`, `"state-test"`, `"titanic"`, or `"violence"`, with others likely to be added later. You can then use these datasets to follow along with any of the examples in the book.
